% Created 2025-01-10 Fri 10:12
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\date{}
\title{}
\begin{document}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}
%----------HEADING----------
%% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%%   \textbf{\Large Troy Fischer} & Email : \href{mailto:troytfischer@gmail.com}{troytfischer@gmail}\\
%%   \href{https://troyfischer.net}{https://troyfischer.net} & Mobile : 772-678-2026 \\
%% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Troy Fischer} \\ \vspace{1pt}
    \small 772-678-2026 $|$ \href{mailto:troytfischer@gmail.com}{\underline{troytfischer@gmail.com}} $|$
    \href{https://www.linkedin.com/in/troy-fischer-805661186/}{\underline{linkedin.com/in/troy-fischer}} $|$
    \href{https://github.com/troyfischer}{\underline{github.com/troyfischer}}
\end{center}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Florida}{Gainesville, FL}
      {Bachelor of Science in Computer Science}{Aug. 2015 -- May 2019}
  \resumeSubHeadingListEnd
\section{Experience}
  \resumeSubHeadingListStart
\resumeSubheading
      {Software Engineer - Principal}{Jan 2024 -- Present}
      {Capital One}{Chicago, IL}
      \resumeItemListStart
        \resumeItem{Consolidated our current feature computation service down from 5 separate deployments to 1.}
        \resumeItem{Cut our provisioned concurrency costs by 95\% by taking advantage of auto scaling policies.}
        \resumeItem{Decreased the size of our application deployment by nearly 66\% from 28MB to 10MB}
        \resumeItem{Replaced our legacy feature computation service with our new serverless system which is projected to save \$1.5M per year in RTE costs and \$367k per year in database costs.}
        \resumeItem{Improved feature authoring experience with new CLI utilities, enabling live results on local machines.}
        \resumeItem{Modularized feature computation libraries to support flexible installation of any arbitrary set.}
        \resumeItem{Received director level confirmation the organization will move forward with my on demand solution as the target for enterprise standardization.}
      \resumeItemListEnd

   \resumeSubSubheading
    {Software Engineer - Senior Associate}{Feb 2022 - Jan 2024}
    \resumeItemListStart
        \resumeItem{Built solutions for on demand data transformations using serverless AWS infrastructure to drive credit card decisioning processes.}
        \resumeItem{Authored code for multiple AWS lambda deployments from initial design to production release.}
        \resumeItem{Completed a feature launch estimated to save the company \$6M annually by stopping undue credit card rewards.}
        \resumeItem{Implemented the topological sort algorithm to enable dynamic dependency resolution for on demand requests.}
        \resumeItem{Instrumented performance tests using the k6 framework to ensure our service level agreements.}
        \resumeItem{Designed a feature authoring self service framework allowing data analysts to build custom data transformations by translating business requirements to python code.}
    \resumeItemListEnd
\resumeSubheading
      {Software Engineer - Senior Associate}{March 2021 -- Feb. 2022}
      {L3Harris}{Palm Bay, FL}
      \resumeItemListStart
        \resumeItem{Maintained a PHP backend to process command and control requests from a browser based GUI.}
        \resumeItem{Gained experience using JQuery to provide dynamic content updates.}
        \resumeItem{Upgraded our PHP MVC framework from Yii 1.1 to Yii 2.0.}
        \resumeItem{Developed automated test suites for SOAP web services using SoapUI.}
    \resumeItemListEnd
\resumeSubheading
      {Software Engineer - Associate}{July 2019 -- Feb. 2021}
      {Parsons}{Centreville, VA}
      \resumeItemListStart
        \resumeItem{Identified and implemented a solution that improved file upload speeds by 50\% by parallelizing file upload chunks.}
        \resumeItem{Used the Java Kafka API to allow communication between microservices in an event driven architecture.}
        \resumeItem{Maintained an automated test suite using Junit4 and led an initiative towards test driven development.}
        \resumeItem{Standardized API creation using the OpenAPI specification which increased adherence to an MVC architecture.}
      \resumeItemListEnd
\resumeSubHeadingListEnd
\section{Open Source Contributions}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Doom Emacs}{: \href{https://github.com/doomemacs/doomemacs/pull/7105}{\underline{Version Control Bugfix}}} \\
    }}
 \end{itemize}
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\href{https://www.credly.com/badges/6cfa3e1d-b75e-4a53-a16b-acdf66ca04e3?source=linked_in_profile}{AWS Certified Solutions Architect}} \\
     \textbf{AWS Services}{: Lambda, SQS, SNS, Dynamo, S3, Cloudformation, Cloudwatch, IAM } \\
     \textbf{Languages}{: Python, Java, C/C++ } \\
     \textbf{Developer Tools}{: Emacs, git, k6, Jenkins } \\
     \textbf{Libraries}{: pydantic, boto3, httpx, asyncio } \\
    }}
 \end{itemize}
\end{document}
